### 2012-05-23 inst/examples/policycosts/L1.Rmd
updated runs at comperable induced costs, using values from exact_npv

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=FALSE, verbose=TRUE or`

@@

# Policy Costs Baseline 
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 0.0
penalty <- L1(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

>>>>

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="L1/" or`

@@

# Policy Costs L1
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 1.52
penalty <- L1(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

### 2012-05-23 inst/examples/policycosts/L2.Rmd
updated runs at comperable induced costs, using values from exact_npv

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="L1/" or`

@@

# Policy Costs L1
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 1.52
penalty <- L1(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

>>>>

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="L2/" or`

@@

# Policy Costs L2
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 0.7586
penalty <- L2(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

### 2012-05-23 inst/examples/policycosts/fixed.Rmd
updated runs at comperable induced costs, using values from exact_npv

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="L2/" or`

@@

# Policy Costs L2
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 0.7586
penalty <- L2(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

>>>>

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="fixed/" or`

@@

# Policy Costs fixed fee 
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 9.103
penalty <- fixed(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````
